\documentclass[SoftwareQuality.tex]{subfiles}

\begin{document}

\section{Requirements on UnitTests}

\subsection*{RTFM}
\begin{frame}{What is a good UnitTest?} 
\Large
\begin{itemize}
\item  R\visible<2->{eadable}
\item  T\visible<2->{rustworthy}
\item  F\visible<2->{ast}
\item  M\visible<2->{aintainable}
\end{itemize}
\end{frame}


\subsection*{R as Readable}
\begin{frame}{What what does Readable mean?} 
\begin{itemize}
\item   what is tested
	\\{\footnotesize
		test name expresses preconditions, desired result
	}
\item   short
	\\{\footnotesize 
		put common preparations in separate methods
	}
\item   what properties of input are important
	\\{\footnotesize 
		choose variable names carefully
		\\declare and initialize input variables explicitly
	}
\item   what properties of output are important
	\\{\footnotesize 
		choose variable name carefully\\
		simple verification (methods with ''speaking names'')
	}
\end{itemize}
\end{frame}

\subsection*{T as Trustworthy}
\begin{frame}{What what does Trustworthy mean?} 
	\begin{itemize}
		\item   business requirement
			\\{\footnotesize
				Does our code implement a business requirement? 
			}
		\item   technical  	
			\\{\footnotesize 
				does the test really execute the (right) part of the production code?\\
				when failing, does the test fail for the right reason?
				}
			\begin{itemize}
				\item replace dependencies
				\item ''test first''
				\item (almost) no custom logic in tests
			\end{itemize}
	\end{itemize}
\end{frame}

\subsection*{F as Fast}
\begin{frame}{What what does Fast mean?} 
	\begin{itemize}
		\item  Tests can be executed frequently without delaying work (each safe at best).
		\item  sophisticated and potentially slow logic in dependencies must be replaced.
	\end{itemize}
\end{frame}

\subsection*{M as Maintainable}
\begin{frame}{What what does Maintainable mean?} 
	\begin{itemize}
		\item  stable against changes in other units
		\\{\footnotesize 
				replace dependencies
				}
		\item  stable against changes in tested unit
		\\{\footnotesize 
				test single assumption
				}
	\end{itemize}
\end{frame}
\end{document}